\begin{thebibliography}{10}

\bibitem{cascales03}
{\sc Cascales, B., Lucas, P., Mira, J., Pallarés, A., y {Sánchez-Pedreño},
  S.}
\newblock {\em El libro de {\LaTeX}}.
\newblock Pearson/Prentice Hall, 2003.

\bibitem{cascales00}
{\sc Cascales, B., Lucas, P., Mira, J.~M., Pallarés, A., y
  Sánchez-Pedreño, S.}
\newblock {\em {\LaTeX{}}. Una imprenta en sus manos}.
\newblock Aula Documental de Investigación, 2000.

\bibitem{goos04}
{\sc Goossens, M., Mittelbach, F., and Samarin, A.}
\newblock {\em The {\LaTeX{}} companion}, 2nd~ed.
\newblock Addison-Wesley Reading, MA, 2004.

\bibitem{goos07}
{\sc Goossens, M., Rahtz, S., and Mittelbach, F.}
\newblock {\em The {\LaTeX{}} graphics companion}, 2nd~ed.
\newblock Addison-Wesley Reading, MA, 2007.

\bibitem{grat99}
{\sc Grätzer, G.}
\newblock {\em First steps in {\LaTeX}}, 1st~ed.
\newblock Springer Verlag, 1999.

\bibitem{grat07}
{\sc Grätzer, G.}
\newblock {\em More math into {\LaTeX}}, 4th~ed.
\newblock Birkhauser, 2007.

\bibitem{kopka04}
{\sc Kopka, H., and Daly, P.}
\newblock {\em A guide to {\LaTeX}}, 4th~ed.
\newblock Addison-Wesley, 2004.

\bibitem{lamport94}
{\sc Lamport, L.}
\newblock {\em {\LaTeX}: A document preparation system}, 2nd~ed.
\newblock Addison-Wesley, 1994.

\bibitem{lange1998programming}
{\sc Lange, D.~B., and Mitsuru, O.}
\newblock {\em Programming and Deploying Java Mobile Agents Aglets}.
\newblock Addison-Wesley Longman Publishing Co., Inc., 1998.

\bibitem{larman1999uml}
{\sc Larman, C.}
\newblock {\em UML y patrones}.
\newblock Pearson, 1999.

\bibitem{oetiker06}
{\sc Oetiker, T., Partl, H., Hyna, I., and Schlegl, E.}
\newblock {\em The not so short introduction to {\LaTeX2e{}}}, 2006.

\bibitem{salido15}
{\sc Salido, J.}
\newblock Curso de {\LaTeX2e{}}.
\newblock {URL:} \url{http://visilab.etsii.uclm.es/?page_id=1468}, 2015.
\newblock Último acceso: 7 sep. 2021.

\bibitem{wikibookLaTex10}
{\sc WikiMedia}.
\newblock {\LaTeX{} Wikibook}.
\newblock {URL:} \url{http://en.wikibooks.org/wiki/LaTeX}, 2010.
\newblock Último acceso 23 feb. 2011.

\end{thebibliography}
